Transcriptomic Analysis for Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-07-06 main.tex
Updates from Overleaf

\usepackage{array}
\usepackage{ragged2e}
\usepackage{rotating}
\usepackage{tabularx}
\usepackage{makecell}
% \usepackage{array}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{hhline}
\usepackage{siunitx} % for  1e-10 scientific notation
%\usepackage{caption}
%\usepackage{subcaption}
\usepackage{booktabs, multirow} % for borders and merged ranges
\usepackage{soul}% for underlines
%\usepackage[table]{xcolor} % for cell colors
\usepackage{changepage,threeparttable}

@@

%\begin{MyColorPar}{red}
TCGA HNSCC cohort was applied for exploration of the biomarker candidate.
A total of 9416 Kaplan-Meier plots (under sliding-window cutoff selection) with associated Cox's univariate and multivariate tables were generated by Cox modeling (see Figure ~\ref{fig:figure1}) and justified by the ranking of hazard ratios.
%By uncorrected P-value below 0.05, we selected 967 genes in which \acrfull{hr} is greater than 1.5 or less than 0.5 (see Figure \ref{fig:figure2}(a) univariate, and Figure \ref{fig:figure2}(b)  multivariate plots). 
The 967 out of 9416 genes were kept by criteria of Kaplan-Meier \textit{P} value ($< 0.05$) and \acrfull{hr} derived from Cox's model (please see Figure \ref{fig:figure2}(a), (b), initial trial).
In the next step, a Bonferroni P-value correction was used to yield 20 genes, under the stringent criteria (see Figure \ref{fig:figure2}(c), (d)).

>>>>

\usepackage{array}
\usepackage{ragged2e}
\usepackage{rotating}
\usepackage{tabularx} % for resizebox?
\usepackage{makecell}
% \usepackage{array}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{hhline}
\usepackage{siunitx} % for  1e-10 scientific notation
%\usepackage{caption}
%\usepackage{subcaption}
\usepackage{booktabs, multirow} % for borders and merged ranges
\usepackage{soul}% for underlines
%\usepackage[table]{xcolor} % for cell colors
\usepackage{changepage,threeparttable}

@@

%\begin{MyColorPar}{red}
TCGA HNSCC cohort was applied for exploration of the biomarker candidate.
A total of 9416 Kaplan-Meier plots (under sliding-window cutoff selection) with associated Cox's univariate and multivariate tables were generated by Cox modeling (see Figure ~\ref{fig:figure1}) and justified by the ranking of hazard ratios.
%By uncorrected P-value below 0.05, we selected 967 genes in which \acrfull{hr} is greater than 1.5 or less than 0.5 (see Figure \ref{fig:figure2}(a) univariate, and Figure \ref{fig:figure2}(b)  multivariate plots). 
The 967 out of 9416 genes were kept by criteria of \acrshort{fdr}-adjusted Kaplan-Meier \textit{P} value ($< 0.05$) and \acrfull{hr} derived from Cox's model (please see Figure 2(a), (b), initial trial).
In the next step, a stringent Bonferroni P-value correction was used to yield 20 genes (please see Figure \ref{fig:figure2}(c), (d)).
%, under the stringent criteria (see Figure \ref{fig:figure2}(c), (d)).

### 2021-07-06 main_redMarked.tex
Updates from Overleaf

\begin{MyColorPar}{red}
TCGA HNSCC cohort was applied for exploration of the biomarker candidate.
A total of 9416 Kaplan-Meier plots (under sliding-window cutoff selection) with associated Cox's univariate and multivariate tables were generated by Cox modeling (see Figure ~\ref{fig:figure1}) and justified by the ranking of hazard ratios.
%By uncorrected P-value below 0.05, we selected 967 genes in which \acrfull{hr} is greater than 1.5 or less than 0.5 (see Figure \ref{fig:figure2}(a) univariate, and Figure \ref{fig:figure2}(b)  multivariate plots). 
The 967 out of 9416 genes were kept by criteria of Kaplan-Meier \textit{P} value ($< 0.05$) and \acrfull{hr} derived from Cox's model (please see Figure \ref{fig:figure2}(a), (b), initial trial).
In the next step, a Bonferroni P-value correction was used to yield 20 genes, under the stringent criteria (see Figure \ref{fig:figure2}(c), (d)).

>>>>

\begin{MyColorPar}{red}
TCGA HNSCC cohort was applied for exploration of the biomarker candidate.
A total of 9416 Kaplan-Meier plots (under sliding-window cutoff selection) with associated Cox's univariate and multivariate tables were generated by Cox modeling (see Figure ~\ref{fig:figure1}) and justified by the ranking of hazard ratios.
%By uncorrected P-value below 0.05, we selected 967 genes in which \acrfull{hr} is greater than 1.5 or less than 0.5 (see Figure \ref{fig:figure2}(a) univariate, and Figure \ref{fig:figure2}(b)  multivariate plots). 
The 967 out of 9416 genes were kept by criteria of \acrshort{fdr}-adjusted Kaplan-Meier \textit{P} value ($< 0.05$) and \acrfull{hr} derived from Cox's model (please see Figure 2(a), (b), initial trial).
In the next step, a stringent Bonferroni P-value correction was used to yield 20 genes (please see Figure \ref{fig:figure2}(c), (d)).
